A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-23 rr-flow.Rmd
swapped order of authors added hash example

author: 
  - name          : "Andreas Brandmaier"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"
  - name          : "Aaron Peikert"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "2"
    institution   : "Humboldt-Universität zu Berlin"

@@

We believe that for sufficient chances of reproducibility, proper documentation is crucial since it answers the question "What steps have to be taken to reproduce the results?". The most precise documentation is computer code, and the most productive computer code is code that runs automatically without human interaction. These principles are what guides the use of `rmarkdown`, `git`, `make`, `docker` and their interaction.

The first step towards reproducibility is to have an R-script or R-markdown, that runs on the own computer without error. A process, we assume, that is familiar to the reader. A next step is to make sure that all files relevant for the analysis can be moved to another computer. To archive that it is essential that all files are within one folder (and subfolders within it) and all paths are relative to that folder. A friendly solution to that problem are [Rstudio Projects](https://r4ds.had.co.nz/workflow-projects.html) and the `here` package.

@@

Sometimes external requirements mean that the data cannot be stored and shared with the scripts. In most of the cases we have seen, these are either space constraints or privacy considerations. In these cases, of course, unrestricted reproducibility is not guaranteed. If this way of dividing data and scripts into different databases is unavoidable, we recommend that you crosscheck using checksums before loading data. To do this, a checksum must be created and filed at the time of the original analysis, and at the time of reproduction the current checksum must be compared with the filed checksum.

! TODO - Beispiel einbauen?

@@

>>>>

author: 
  - name          : "Aaron Peikert"
    affiliation   : "1,2"
  - name          : "Andreas Brandmaier"
    affiliation   : "1,3"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    email         : "brandmaier@mpib-berlin.mpg.de"

affiliation:
  - id            : "1"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "2"
    institution   : "Humboldt-Universität zu Berlin"
  - id			  : "3"
  	institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany & London, U.K."

@@

We believe that for sufficient chances of reproducibility, proper documentation is crucial since it answers the question "What steps have to be taken to reproduce the results?". The most precise documentation is computer code, and the most productive computer code is code that runs automatically without human interaction. These principles are what guides the use of `rmarkdown`, `git`, `make`, `docker`.

The first step towards long-term reproducibility is to have an R-script or R-markdown, that runs on a local computer without error. A process, we assume, that is familiar to the reader. A next step is to make sure that all files relevant for the analysis can be moved to another computer. To this end, it is essential that all files are within one folder (or, subfolders within it) and all paths are relative to that folder. A robust solution to the problem of making sure that file access does not break across computing platforms are [Rstudio Projects](https://r4ds.had.co.nz/workflow-projects.html) and the `here` package.

@@

@@

Sometimes external requirements mean that the data cannot be stored and shared together with the scripts. In most of the cases we have seen, these are either space constraints or privacy considerations. In these cases, of course, unrestricted reproducibility is not guaranteed. If this way of dividing data and scripts into different databases is unavoidable, we recommend that you crosscheck using checksums before loading data. To do this, a checksum must be created and filed at the time of the original analysis, and at the time of reproduction the current checksum must be compared with the stored checksum (also called a "hash", e.g., using the functions provided in package `digest`).

```{r}
x <- data.frame(VAR1=c(1,2,3,4),VAR2=c(0,4,6,9) )
digest::sha1(x)
```
